\chapter{User Study Survey}

Following questioner resembles in term of wording and possibilities for responses but it is not the actual one that has been conducted during the user study.

\section{Demographic Questions}

In the start of survey participant were asked about their demographic information that allows statements about the sampled population.
\newline \newline
\textbf{Question:} Select age group?\newline
\textbf{Answer:} Between 12 to 18 | Above 18 to 35 | Above 35
\newline \newline
\textbf{Question:} Primary profession?\newline
\textbf{Answer:} Student | Employee | Self-Employed | Other  (free text)
\newline \newline
\textbf{Question:} How often do I cook?\newline
\textbf{Answer:} Daily | Once in a week | Twice in a week | 3 to 5 times per week | Occasionally

\section{Testing Framework}

The data points directly related to the testing framework are split into statements rated on 5-point Likert scales, data measures, regular questions \newline

\subsection{Likert Scale Statements}
These are statements where participants indicated their rate of approval on a 1-5 point Likert (discrete) scale. Instead of the actual values text representations were shown, they are mapped as follows:\newline
1 Strongly Agree | 2 Agree | 3 Neutral | 4 Disagree | 5 Strongly Disagree\newline
Some statements measure the level of disapproval. Here the mapping is reversed (5, strongly agree to 1, strongly disagree).\newline \newline
\textbf{Perceived Reciprocity}\newline 
\textbf{Question:} Which system do you think helps more to select a recipe?\newline
\textbf{Answer:} Recipes with all graphical and textual informaiton | Recipes with little graphical and textual informaiton. \newline \newline
\textbf{Perceived Scarcity}\newline
\textbf{Question:} Filtering of recipes with respect to course helps me in recipes finding according to meal time.\newline \newline
\textbf{Perceived Authority}\newline
\textbf{Question:} Recipe star rating helps me in selection of recipe.\newline \newline
\textbf{Perceived Social Proof}\newline
\textbf{Question:} I understand that rating a recipe not only helps me to receive better recommendations but also the whole community?\newline \newline
\textbf{Perceived Liking}\newline
\textbf{Question:} For critiquing a recipe which method do you prefer?\newline
\textbf{Answer:} By critiquing on both ingredients and recipe | By critiquing only on recipes | Neither. \newline
\textbf{Perceived Commitment}\newline
\textbf{Question:} An Explanation of a recommended recipe would motivate me to cook that recipe.\newline \newline
\textbf{Perceived Efficiency}\newline
\textbf{Question:} In which test run did the recipe items reflect according to your preference?\newline 
\textbf{Answer:} Run 1 | Run 2 | Run 3 | Run 4 | Run 5 | Other  (free text).\newline \newline
\textbf{Question:} Looking for a recipe using this app required too much effort.\newline \newline
\textbf{Perceived Transparency}\newline
\textbf{Question:} I understand what the system bases its recommendations on.\newline \newline
\textbf{Perceived Scrutability}\newline
\textbf{Question:} I find it easy to correct any wrong assumptions made by the recommender.\newline \newline
\textbf{Perceived Satisfaction}\newline
\textbf{Question:} I am satisfied with the recipe, I last selected and would like to cook.\newline 
\textbf{Question:} Overall, I am satisfied with the recommender.\newline \newline
\textbf{Perceived Overall Control}\newline
\textbf{Question:} I feel in control of telling the system what I want.\newline
\textbf{Question:}I liked the design of the application.\newline
\textbf{Question:}I understood quickly how to use the app.\newline \newline
\textbf{Perceived Contextual Information}\newline
\textbf{Question:} Which of the following things motivate me to cook a recipe?\newline
\textbf{Answer:} Calories infomation | Contextual information (e.g. Cooking time, Recipe Course) | Other  (free text).\newline \newline
\textbf{User Preference}\newline
\textbf{Question:} I would use the app I just tested for finding recipes. \newline 
\textbf{Question:} Which system do you like most in terms of explanation? \newline
\textbf{Answer:} Explanation having calories, my liked ingredients in it. | I don't need explanation in recipe detail..\newline
\textbf{Question:} What are your reasons for not using that app in the future? \newline
\textbf{Answer:} Privacy concerns | None | Other  (free text).
