\chapter{Evaluation And Conclusion}

Despite the fact, how good the prototype in terms of algorithmic and design approaches. There will be some probability that elaborates, users are doing what they are not expected to do.  This leads to other features(s) that needs to be develop in order to improves the user’s satisfaction and increase his willingness to user the system. Therefore it is important that developed system should go through an evaluation proves before it goes live. Focus of evolutions to ensure that product is appropriate and the involvement of user through the design process. This chapter depicts the evaluation of prototype in a real user study and present the result.

\section{Motivation and Goals}

Motivation behind performing evaluation to determine, whether the process of recipe according to user interest in mobile critique-based recommender system can be improved by applying Persuasive Principles. As discussed earlier, purpose of developed Food Recommender System aim to be used in a real world situation. This established some aspects of the user study, including the development of a variant of the proposed application and assessment of the system.\newline

During the study, two variants of the system will need to be tested, one begin the basic interface design, without explanation and works on basic recommender system by providing star rating to the recipes. Whereas, the second system is the main output of thesis, with better infrastructure of recipes, sleeker interface and having explanation about the recipes. Additionally recommender system algorithm supports critiquing on both ingredients and recipes.\newline 

The study is designed in a way that each user has to test both variants of the application, which system is more appealing for the users. Focusing on real effect of recommendation depends on factors like user intent, context, way to present recommendations set and other. Thus experiment needs to provide evidence as the true value of evaluation.\cite{shani2011evaluating}. Additionally a single irritation of user study should not exceed with more then 20 min to maintain user interest. Considering the fact that user have to test two variant of application. However it is possible that user might have get some less qualitative results which is not due the fault from the system but because users were overwhelmed with long sessions.  \newline

The focus of evaluation was to measure the effect of persuasion by providing the recommendation in form of recipes. Also how active learning also system to change itself according to user preferences. However it exclude the non-relevant part like ingredients integration to improve the recipes.

\section{Data set Generation}

Data sets are necessary to create a pragmatic setup to represent a real world objects. Therefore, a data crawler needs to be developed as an open-source project that will crawl the recipes form any recipe data bank. Crawler developed by us is written in java.  Crawling recipe form data bank is a two steps process.  First fetches the recipes from databank on behave of food type and course.  In second step it will sync all those recipes whose details are not present in our database. Additionally recipes images are not been stored in our system instead of saving image we stores their URLs. Extracted data provide international recipes of different cousins. However, it provides functionally to add more different data source that provides recipes. To keep the amount of work reasonable items were associated with the following:

\begin{enumerate}
	\item Unique identifier for recipes
	\item 11 types of courses (e.g,. Appetizers, Bread)
	\item 91 Cuisine (e.g. American, Thai, Beverages)
	\item Images links of different sizes
	\item Preparation
	\item List of ingredients
	\item Popularity of recipe
\end{enumerate}

Currently our data bank has 1303 of recipes, 10037 ingredients. Furthermore, it can grow more depends on crawling method.

\section{Setup}

This section leads our discussion toward the selection of test hardware, different variants of application and testing framework for the sake of performing evaluation.

\subsection{Test Hardware}

Recommended hardware must have at least 320x 480 resolution and above, running iOS version 8.0 or later. In order words required device to run application is iPhone 4S and above.  

\subsection{Variants}

Two variants of system are developed to test. Both variants use the same recommendation algorithm. However they are different to each other by have unique interface design, explanation of recommendation and critiquing methodology. 

\begin{enumerate}
	\item \textbf{Experiment (EXP)} This variant refers to the proposed developed system as discuss in chapter 4. It allows users to change their preferences while interacting to the system by critiquing on ingredients and recipes. System provides explanation to each recommended item. Additionally interface follows the user centric design, which contains more information about the recipe to draw user attention towards recipes.
	
	\item \textbf{Basic (BASE)}  Consider as baseline to compared the needs and effectiveness of actual system. In this system mostly provides textual information about the recipe. User can critique only recipes by given stars. System does not provide any explanation along with recipes. 
\end{enumerate}

\subsection{Testing Framework}

Testing framework that is applied in user study is a subset of the aspect that are relevant for persuasion and critiquing in recommend system. It follows the user-centric design approaches \cite{pu2006trust} and framework that applied for evaluation of recommend recommendation system \cite{shani2011evaluating}. Measure data is divided into following areas:

\subsubsection{Persuasion’s Principle}

Persuasion’s principle that discussed in section \ref{ch4_persuasion_explaination} were related to the how these factors will be implemented in our system.  It is essential aspect for this thesis that the recommendations that are suggested to user should ne persuasive in nature and follows the principle. The forth-coming discussion relates whether user might be able to perceive those or not.

  \begin{enumerate}
  	\item \textit{Perceived Reciprocity} is allows user to return his favor by critiquing as recipe and select other good food according to particular food course and cuisine. The participants were asked they think that system helps them to select them a recipe although this recipe his according to his preferences, but the system consider other user feedback on that recipes before making up recommendations.
  	
  	\item \textit{Perceived Scarcity} measurement indicates by categorizing recommendation with respect to context and consumption time of recipe. Participants were asked whether they find that system helps them to filter out the recipe according to their meal time.      

  	\item \textit{Perceived Authority} refers to the popularity of a particular recipe in a given context of user. To measure the level of perceived authority, Participants were asked to what ascent they felt authority. 
  	
  	\item \textit{Perceived Liking} refers to factors that include liking a recipe. In our system measure matric was based on ingredients and recipe staring. Participants were asked which mechanism like/dislike help more in finding out the recipe. 	  
  	
  	\item \textit{Perceived Commitment} indicated to what degree system is committed to user preference. In order to measure the degree of commitment metric is defined. Participants were asked to mark if they felt that system is committed to preferences or not.	  
  	  	
  	\item \textit{Perceived Social Proof} denotes the what society think about that particular item in our case recipe. User may or may not thought that social factor is present, By asking the user to what level they consider social factor is present in our system by providing them a scale.   
  \end{enumerate}
  
\subsubsection{Transparency}

Ability of a system that allows user to understand its working and explain system choices and behavior. However it is possible that user’s understanding about the system working might be differ form its actual working. For the sake of evaluation user were asked to mark choices that they think about the system when making recommendations. \newline

\textit{Perceived Transparency:} There is a possibility that user might or not perceive that system is transparent. By asking the factors which users thinks system include while making a recommendation. It is possible learn their perceived transparency.


\subsubsection{User Control}
Level of control that provides to users while operation a system refers to User Control. Under this sub section we want to measure the following items:  \newline

\textit{Perceived Overall Control} indicates that does user have overall control over recommendation. The participant were asked about what they feel about while using the application by rating that were they able to tell about the system which recipes are the looking for, telling their preference to system and finally to what assent they feel they have control over system. \newline

\textit{Perceived Scrutability} denotes the ability of the system that allows user to revised their preference and excludes those assumptions that system made on there behaves. Participants were asked to rate till what ascent they feel control over system to correct the wrong assumption made by the system.

\subsubsection{Efficiency}

Providing good recommendation is not only the task of recommender systems. Also it is essential for a system how quickly it come to decisions that help in selection of item especially in the domain of mobiles. Measuring efficiency is divided into two perspectives. First, as in conversational recommender numbers of cycles were counter.  Where each cycle defined as number of times user have to perform update his preference in order to complete a task. Each cycle have an impact on user model. Second refers as time that passed from display of first recommendation set to selection and confirmation of required item. Where time measure in seconds.\newline

\textit{Perceived Efficiency} Duration of item until item found is hard to perceive for user. Therefore for the sake of simplicity user were asked if it requires to much effort to find a recipe they are looking for. Additionally run of cycles are also hard to reminder but since conversation system cycle normally cycle are not be exceed to two cycle. Therefore user were asked to mention in which cycle they received their recipe. 

\subsubsection{Satisfaction}

Satisfaction is the ability to make system fun while user is interacting with the system. Also providing poor recommendation decrease the user interest.\newline

\textit{Perceived Satisfaction} measure to determine user’s feeling while in using system. It allows user to express their preferences about the system in a direct way. Participants were asked to which ascent they were satisfied about they system.

\subsubsection{Context}

Context defines as any information that can be used to characterize the situation of entity. It is important for recommendation to consider the context while making a recommendation in order to make the recommendation more concrete. \newline

\textit{Perceived Context} are determine in following ways: calories information about the recipe,  cooking time and course of recipes. Participants were asked to select which contextual information helped them to select to recipe. 

\subsubsection{UserDemographic}

Participants were asked to fill their demographic information for instance age, occupation, how often they cooked. 

\subsection {Testing Procedure}

\section{Results}

\section{Discussion}
