\chapter{Introduction}
\pagenumbering{arabic}%Ab hier, werden arabische Zahlen benutzt
\setcounter{page}{1}%Mit Abschnitt 1 beginnt die Seitennummerierung neu.
\thispagestyle{empty}

The motivation behind this Master Thesis is to implement and evaluate a Healthy Food Recommendation System for Mobile. In the beginning, it provides overview and give the reasoning about the selection of system. Relevant background and related work is presented, Followed by the development and design process together with the evaluation process will be presented. \newline
This chapter will enlighten the motivation behind developed system in Section 1.1. Followed by goals in Section 1.2. Whereas Section 1.3 will provide a brief outline on structure of thesis.

\section{Motivation}\label{motivation}

Rapid innovation and significant advancement in the field of technology and scientific research has made smartphone a primary computing and communication device. Smartphone is now become a necessity of life and people use it as an assistant for their day to day work. According to latest survey more than half of Internet traffic is accounted by mobile device. Enhancement in communication technology and flexible data option provided by network operators has increase relevance of interactive mobile applications. Packed with hundreds of features smartphone use different applications for variety of functionalities which required internet connectivity. Furthermore, smartphone support touch screen and rich support of multimedia and other application take the user experience to the next level.\newline

Suggestions are the important factor of our day-to-day life. From watching a movie, to cooking and to on shopping. We need valuable advice. Recommendations are always helpful in choosing a better alternative. It not only save time but also minimize the individual's effort.\newline

Recommender system are increasingly popular now are days. Form e-comers to movie websites, they not only help to increase business but also behave an personalize user preference assistance. Another aspect of describing Recommend system is filtering technology that user to filter suggests the information to user according to his taste. In order words we can also say that Recommender systems are the smart search engine, which suggest result by, compare different items with each other. Research and advancement are going on this domain in order to improve the quality of recommendations. \newline 
The most important goal for recommendation system designers is user willingness to peruse recommendation provided by the system. Fundamental process of recommendation is finding and conceptualizing relationship of item, current context and how the message is communicated, opens up the way of persuasiveness in recommendations.\newline

Services provided by recommendation system through e-commerce to cooking are numerous in nature. Searching of products returns an overwhelming set of options. For instance, Comparing and Filtering of products among irrelevant set and find the suitable product. Such techniques work fine with web interface, whereas, smartphones they are not very useful due to hardware limitations. Critique-based recommendation helps in revision and acquisition of user preference, in order to improve quality of recommendations.\newline

One the basic need is Food among human. Good health represents proper dietary habit. However, diet plan is always based on person’s physical conditions like gender, weight, age and health status. Furthermore, taste and food preference is differ among individuals. Therefore, creating balance dietary plan based on individuals taste and health preference is always challenging.\newline

The World Health Organization \cite{world2008information} is predicting that the number of obese adults worldwide will reach 2.3 billion by 2015 and the issue is attracting increased attention. Therefore, electronic food management systems have become a hot topic and, are under consideration to replace traditional paper based program. Idea of using electronic devices for health related matter is not new; similar devices are in use by patients for medical reasons e.g. Glucometer, and blood pressure monitor. People want, to carry better life style and to live healthy. Therefore popularity of food monitoring systems is getting popular.  These systems are not only providing valuable services but hold user preferences and keeps history to provide more personalize recommendations. Recommendations are based on food ratings and browsing histories.\newline

Food recommendations have gotten a tremendous amount of success and still in research phase for further improvement. Along with significant advancement and feature set like similar recipes, recipe nutrition detail, where to buy ingredients from some research, some wholes are still remaining. Indeed recommendation techniques like collaborative, content and knowledge based filtering are good for job done. But food domain is not quite simple. User preference and taste not only change by their mood but much more depend upon their health. Therefore, Active learning and critiquing techniques are required to improve better recommendation. So that user can give their feed back and get what ever his preferences are. Mostly approaches are done critiquing by using rating of recipes and generate their result by using celebrative or content based filtering. Similarly, knowledge based filter digs some more; here rating is based on ingredients. Furthermore, persuasion of recommendation is always not guarantied in all cases. Clearly the system is not able to provide the best recommendations due to its detachment from the current situation; what is lacking in these approaches are intersection of persuasiveness, active learning and critiquing and last but not the least user preference context.\newline

This work focuses on generation of health food recommendation on a mobile platform. Recommendation relies on user context, which allow user to critique, based on ingredients and recipes depends on his health and taste through which system will perform active learning. Lastly all recommendations should be persuasive in nature. in order to achieve persuasiveness in recommendations, we focus on user interface and the explanation of recommendation. Which helps user to get an idea why system generates this recommendation to me.\newline

The following short description of the target scenario will illustrate the driving idea behind this research project.\newline

 \textit{John is a software engineer and very health conscious. He has a tight schedule due to work and gym but loves to cook. He wants to keep track of his diet depends on his taste and preferences. Furthermore, he wants try out some new food base on his time schedule}\newline

\section{Goals}

On the basis of scenario, describes in last section, this work reflects the goals which are stated below:\newline

A recommendation is valuable if it interests the user. To determine the generated recommendation is according to user interest entails to our first primary goal, which is offering Persuasive recommendations. Major factors should be considered before given suggestion is Message and Source. Therefore our Second goal is to implement Active Learning and Critiquing approach to justify our suggestion. Since Critiquing relies on context that’s why it is important to understand the Consumption and Accessibility context which infers our third goals.  Similarly understanding the food ontology refers in scenario helps us to understand forth goal of system. Finally how the user will interact with his device conveys our last goals, which is Mobile user interface.\newline

To achieve primary goals there are several other interesting secondary goals, which facilitate, how our primary goals should be achieved. Starting with the research phase, which includes question and answers to user how they want to use such system in order to achieve better usability. Next focus on existing search work how the other system implements food recommendation scenarios, finding out what are their weakness and strengths. Food ontologies understanding how they are interrelate with other. What factor in which recipes are dependent on in order to develop strong system. Understanding user context which time he prefers which recipe. Furthermore, it is important to research on what researches and related work are out there under Persuasive and Active learning and Critiquing system to grab the understanding, how we can get inspiration from their valuable approaches and work. Finally focus on user experience of such application is one of challenging task, how and where to show the important aspects of recipe in our interface, so that it is easy to learn and has improved usability in comparison with current market applications.\newline
Once the research phase has done next step to collect the functional and non-functional requirement of the system, which is collected by interviewing friends and family voluntaries. Once the system is build it has been tested with gathered functional and non-functional requirement and find out the limitation or boundary conditions of system. More over iOS client needs to be test with given requirement additionally user satisfaction should be required for usability test.\newline

Finally, evaluation of developed prototype by user study. In order to clarified the methodologies and processes followed by our selected approaches. After finishing the evaluation reflected results leads to potential improvements and opens up the new direction of research.\newline

\section{Outline}

Division of this thesis is split up into six chapters. \textit{Chapter1} contains introduced the ideas, motivations and goals.\newline

\textit{Chapter2} starts with background in which some definitions and classification of recommendation systems, Followed by different types of profiling and contexts that impact on recommendations. Furthermore, in related work section, pervious work of Persuasiveness, Critiquing and Personalized food recommendation techniques have been discussed.\newline

\textit{Chapter3} explains the Profiling and Context in details along with factors of recommendations. Moreover it covers algorithms that are used to develop the system.\newline

\textit{Chapter4} discuss the System design and architecture phase, which hold the all ERD, components view, servers on which system depend. In the end of the chapter API calls are mentioned which are provided by server.\newline

\textit{Chapter5} elaborates how the user study has been conducted by mentioning the goals, methods, and testing framework along with the dataset. In the end of this chapter measured results and discussion is mention.\newline
  
\textit{Chapter6} will summarizes the achievements and gives clues about further development and research.\newline
