
\chapter{System Components}

This chapter will provide the explanation about the components of the system it and their attributes. It will also highlight how they intereact with each other in order to achieve the goals of this thesis. The chapter begins with explanation of profiling approaches, followed by impacts of context, critiquing and persuasion.

\subsection{User Profile}

One the goal of a system is to recommend user food that suits to his preferences which can be gatherd by profiling a user. In our system we followed a hybrid approach to build a user profile. Demographic information of a user is implicitly fetch from his Facebook account. The reason behind following implicit profiling approaches is to get user information without bothering them. This allows system to  have up to date information about them.  However, it has been noticed that people are reluctent to those systems that request permission to access their social network activity information. Knowing these concerns, we only ask users to permit access to their basic information. Following are the acquired attributes from Facebook profile.

\begin{enumerate}
	\item Birthday
	\item Email	
	\item FirstName
	\item LastName
	\item Gender
	\item Name
	\item Profile Link
	\item UserId
\end{enumerate}

Moreover, explicit profiling techniques are used to gather contextual information and his preference about the food but there exists some problems in this technique. It demands user’s time and willing to provide the data and by filling the long forms which is quite boring in the eyes of users. Since our system Knowledge based Personalized recommender system we have to deals this problem in a very efficient manner because system recommendations will totally depends on user feedback. Therefore we minimized the form-based approach to just simple by providing simple toggling, rating and selection mechanism. We totally avoid the form-based approaches and split up the information according to concerns screen of the application in order to get better results.

\subsection{Food Profile}

\section{Contexts}

\subsection{Consumption Context}

\subsection{Accessibility Context}

\chapter{Critiquing}

\section{Persuasion}