\chapter{\abstractname}

%TODO: Abstract


This thesis presents the concept of impact of Persuasive mobile recommender system in lifestyle domain. It combines the previous research in Persuasive recommendation system, Active Learning and critiquing. It is tailored to one the leading smartphone mobile platform, exploits the benefits of mobile environment by following the user interface guidelines to overcome the challenges comes with limited screen sizes.\newline

Explanations in recommender systems play a role of motivator, which influence on consumers to opt recommendation item. In past, explanations were used as one-way communication. System does not use them to get user feedback and doesn’t have any impact on user decision. The system developed in this thesis generates personalized explanation that has an impact on user decision. Generated recommendation considers on user’s preference and context. In addition to this system allow the user to critique on recommended item so that system can learn more about use and correct its wrong assumption. \newline

An iOS application was developed, that rely upon the Principles named as Cialdini’s Influence Principles, a framework that is well tested and verified. The purpose behind using this approach because it enrich the recommendation with explanation and also allows examining their impact on persuasiveness. Also evaluate the explanation in terms of transparency, user control, perceived efficiency and user acceptance.  In addition to this application follows existing research of Active Leering Critiquing methodology to learn about user preferences.   The resulting application was evaluated by the diverse set of users.
